Lesson 4
========================================================


### 探索两个变量

***

### Scatterplots and Perceived Audience Size
Notes:
散点图适用于研究两个连续变量之间的关系
***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv",sep = "\t")
# 还可以使用以下代码读入数据
# read.delim("pseudo_facebook.tsv")



ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point()

# 等效的qplot语法
# qplot(x = age, y = friend_count, data = pf)
  
```

***

#### What are some things that you notice right away?
Response:
25岁左右的用户拥有最多的好友数量
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
# qplot 
qplot(x = age, y = friend_count, data = pf)

# ggplot 与 qplot之间的主要区别是：
# 1. 我们需要geom指定图表类型
# 2. ggplot需要将xy变量用aes包裹
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point() +
  xlim(13,90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13,90)

ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13,90)
```

#### What do you notice in the plot?
Response:
多数用户好友少于1000
***

### Coord_trans()
Notes:

```{r Coord_trans()}
# 抖动可能会给每个点添加正的或负的噪声
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20,position = position_jitter(height = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20,position = position_jitter(height = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(color = "Red", alpha = 1/10, position = position_jitter(height = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:
D Plyr程序包可以让我们分割数据框，然后向某些部分应用某个函数
可能会用到的常见函数包括 filter(),group_by(),mutate(),arrange()

```{r Conditional Means}
library(dplyr) 

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())
head(pf.fc_by_age)

# Another way:
# %>% 可以将函数链接到数据集上
# pf.fc_by_age<- pf %>%
#   group_by(age) %>%
#   summarise(friend_count_mean = mean(friend_count),
#           friend_count_median = median(friend_count),
#           n = n()) %>%
#   arrange(age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean),data = pf.fc_by_age) +
  geom_line(color = "Red")
```

***

### Overlaying Summaries with Raw Data
Notes:
快速探索以及合并原始数据的图形
```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count),data = pf) +
  geom_point(alpha = 0.05,
             position = position_jitter(height = 0),
             color = "red") +
  coord_trans(y = "sqrt") +
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .9),
            linetype = 2, color = "blue") +
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .5),
            color = "blue") +
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .1),
            linetype = 2, color = "blue") +
  coord_cartesian(xlim = c(13,70), ylim = c(0,1000))
```

#### What are some of your observations of the plot?
Response:
90% 的用户好友数量少于1000
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:
进一步汇总年龄与好友数的关系，使用相关系数
***

### Correlation
Notes:

```{r Correlation}
?cor.test()
cor.test(pf$age,pf$friend_count,alternative = "g",method = "pearson")

with(pf,cor.test(age,friend_count,method = "pearson"))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf,age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:
单调关系的度量，如等级相关度量spearman
***
```{r}
with(subset(pf, age <= 70), cor.test(age, friend_count, method = "spearman"))
```



## Create Scatterplots
Notes:

```{r}
# quantile(data, prob.)数据的百分比
ggplot(aes(www_likes_received,likes_received),data = pf) +
  geom_point(color="red") +
  xlim(0, quantile(pf$www_likes_received, .95)) +
  ylim(0, quantile(pf$likes_received, .95)) +
  geom_smooth(method = "lm", color = "black")

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(pf, cor.test(www_likes_received, likes_received))

# 0.948 很强的相关
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:
0.948
***

### Moira on Correlation
Notes:
为什么要首先观察相关性?这能告诉我们关于两个变量的什么信息?

除了生成散点图，可直观观察两个变量的相关性外，通常还会测量其相关系数，来真实量化其相关程度，这一点非常重要。
在处理问题时，做某种回归，即对事物建模，将变量放入回归，回归的一个假设就是这些变量彼此独立，如果所有变量都彼此相关，那么无法判断是那个变量产生的这种现象
因此，首先衡量变量之间的相关性很重要，这可以帮助你确认哪些变量不要一起投入，可以帮助你判断实际上要保留那些变量
***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}
data("Mitchell")
?Mitchell

ggplot(aes(Month, Temp),data = Mitchell) +
  geom_point(color = "red")
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Month, Temp))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(Month, Temp),data = Mitchell) +
  geom_point(color = "red") +
  scale_x_continuous(breaks = seq(0,203,12))
```

***

### A New Perspective

What do you notice?
Response:
6,7月份温度最高
Watch the solution video and check out the Instructor Notes!
Notes:
The cor and cor.test functions determine the strength of a linear relationship, but they may miss other relationships in the data.


***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(age, friend_count_mean), data = pf.fc_by_age) +
  geom_line()

pf$age_with_months <- with(pf, age + (1- dob_month/12))


```

***

### Age with Months Means

```{r Age with Months Means}
# Another way:
# %>% 可以将函数链接到数据集上
# pf.fc_by_age<- pf %>%
#   group_by(age) %>%
#   summarise(friend_count_mean = mean(friend_count),
#           friend_count_median = median(friend_count),
#           n = n()) %>%
#   arrange(age)

pf.fc_by_age_months <- pf%>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)

head(pf.fc_by_age_months)
```

Programming Assignment
```{r Programming Assignment}

p1 <- ggplot(aes(age, friend_count_mean), data = subset(pf.fc_by_age, age < 71)) +
  geom_line()

p2 <- ggplot(aes(age_with_months, friend_count_mean), data = subset(pf.fc_by_age_months, age_with_months < 71)) +
  geom_line() +
  geom_smooth()

p3 <- ggplot(aes(round(age/5) * 5, friend_count), 
             data = subset(pf, age < 71)) +
  geom_line(stat = "summary", fun.y = mean)
library(gridExtra)
grid.arrange(p1, p2, p3, ncol = 1)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

