

```{r}
# import data set
library(ggplot2)
dim(diamonds)
```

##  1. 价格与x

```{r}
# Create a scatterplot of price vs x

ggplot(aes(x, price), data = diamonds) +
  geom_point()

```

## 2. 发现- 价格与x
***
除部分x为0的钻石价格，没有看到（0,4）之间的钻石，x=4以后价格与x成线性关系
***

## 3. 相关性
```{r}
# correlation between price and x
with(diamonds, cor.test(x, price))

# correlation betweenn price and y
with(diamonds, cor.test(y, price))

# correlation between price and z
with(diamonds, cor.test(z, price))
```

## 4.价格与深度
```{r}
# create a simple scatter plot of price vs depth

ggplot(aes(depth, price), data = diamonds) +
  geom_point(color = "red")
```

## 5.调整-价格与深度
```{r}
# Change the code to make the transparency of the point to 
# be 1/100 of what they are now and mark the x-axis every 2
# units.

ggplot(aes(depth, price), data = diamonds) +
  geom_point(alpha = 0.01, color = "red") +
  scale_x_continuous(breaks = c(0,80,2))
quantile(diamonds$depth,.95)
```
## 6. 典型深度范围
```{r}
# most diamends are between what value of depth
ggplot(aes(depth, price), data = diamonds) +
  geom_point(alpha = 0.01, color = "red") +
  scale_x_continuous(breaks = c(0, 80))
```

## 7. 相关性-价格与深度
```{r}
# correlation of depth vs price
with(diamonds, cor.test(depth, price))
```
***
Based on the correlation coefficent would you use depth to predict the price of a diamend?
No. The correlation is low
***

## 8.价格与克拉

```{r}
# Create a scatter plot of price vs carat and omit the top 1% carat values
ggplot(data = diamonds, aes(carat, price)) +
  geom_point() +
  xlim(0, quantile(diamonds$carat, .99))
```

## 9.价格与体积
```{r}
names(diamonds)
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
```

## 10.发现-价格与体积
```{r}

ggplot(diamonds,aes(volume, price)) +
  geom_point()

# how many diamends have 0 volume?
library(plyr)
count(diamonds$volume ==  0)
```
***
What are your observations from the price vs volume scatterplot?
Some volumes are 0! There's an expensive diamond with a volume near 4000, and a cheaper diamond with a volume near 900.
***
## 11.子集相关性
```{r}
# what's the correlation of price and volume?
# Exclude diamends that have a vulume of 0 and that are greater than or equal to 800
with(subset(diamonds, volume != 0 & volume < 800), cor.test(volume, price))
```
## 12.调整-价格与体积
```{r}
# Subset the data to exclude diamends with a volume greater than or equal to 800, Also, exclude diamends with a volume of 0.
# Adjust the transparency of the points and add a linear model to the plot.
ggplot(subset(diamonds, volume !=0 & volume < 800), aes(volume, price)) +
  geom_point() +
  geom_smooth(method = "lm")
```
## 13.平均价格-净度
```{r}
# Use the function dplyr package to crate a new data frame containing info on diamends by clarity
# Name the data frame diamendsByClarity
# The data frame should contain the following variables in this order
# 1.mean_price
# 2.median_price
# 3.min_price
# 4.max_price
# 5.n

library(dplyr)



diamondsByClarity <- diamonds %>%
  group_by(clarity) %>%
  summarise(mean_price = mean(as.numeric(price)),
            median_price = median(as.numeric(price)),
            min_price = min(as.numeric(price)),
            max_price = max(as.numeric(price)),
            n = n()) %>%
  arrange(clarity)

head(diamendsByClarity)
```

## 14.平均价格柱状图
```{r}
# We've created summary data frames with the mean price by clarity and color. You can run the code by clarity and color


diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, 
                                    mean_price = mean(price))

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color,
                                  mean_price = mean(price))


# Write a additional code to create two bar plots on one output image using the grid.arrange() function from the package gridExtra
library(gridExtra)

p1 <- ggplot(diamonds_mp_by_clarity,aes(x = clarity, y = mean_price)) +
  geom_bar(stat = "identity")

p2 <- ggplot(diamonds_mp_by_color,aes(color, mean_price)) +
  geom_bar(stat = "identity")


grid.arrange(p1, p2, ncol = 1)


```

## 15.平均价格趋势
***
What do you notice in each of the bar charts for mean price by clarity and mean price by color?
Mean price tends to decrease as clarity improves. The same can be said for color.
