---
output: html_document
editor_options: 
  chunk_output_type: inline
---
Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = "\t")

ggplot(subset(pf, !is.na(gender)), aes(gender, age)) +
  geom_boxplot()

ggplot(subset(pf, !is.na(gender)), aes(gender, age)) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = "point", shape =4)

ggplot(subset(pf, !is.na(gender)), aes(age, friend_count)) +
  geom_line(aes(color = gender), stat = "summary", fun.y = median)

library(dplyr)
pf.fc_by_age_gender <- subset(pf, !is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)

head(pf.fc_by_age_gender)
tail(pf.fc_by_age_gender)

```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

ggplot(pf.fc_by_age_gender,aes(age, median_friend_count)) +
  geom_line(aes(color=gender))

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = "median_friend_count")
head(pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
# Plot the retio of the female to male median firend counts using the data frame pf.fc_by_age_gender.wide


ggplot(pf.fc_by_age_gender.wide, aes(age, female / male)) +
  geom_line() + 
  geom_hline(yintercept = 1, alpha = 0.3, linetype =2, color = "red")
  

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

pf$year_joined <- floor(2014 - pf$tenure/365)

table(pf$year_joined)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
# Create a new variable in the data frame called year_joined.bucket by using the cut function on the variable year_joined
# (2004, 2009],(2009,2011], (2011,2012], (2012,2014]

pf$year_joined.bucket <- cut(pf$year_joined,
                             c(2004,2009,2011,2012,2014))

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}

table(pf$year_joined.bucket, useNA = "ifany")

ggplot(subset(pf, !is.na(year_joined.bucket)), aes(age, friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(subset(pf, !is.na(year_joined.bucket)), aes(age, friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = mean, linetype = 2 )
```

***

### Friending Rate
Notes:

```{r Friending Rate}
firending_rate <- with(subset(pf, tenure >= 1), friend_count / tenure)
summary(firending_rate)
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(subset(pf, !is.na(year_joined.bucket) & tenure >= 1), aes(tenure, friendships_initiated / tenure)) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = mean)

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_smooth(aes(color = year_joined.bucket),method = "lm" , stat = "summary", fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:
```{r}
yo <- read.csv("yogurt.csv")
str(yo)
yo$id <- factor(yo$id)
str(yo)

ggplot(yo, aes(price)) +
  geom_histogram(binwidth = 10)
```

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

summary(yo)
length(unique(yo$price))
table(yo$price)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}


yo <- transform(yo, all.purchases = (strawberry + blueberry + pina.colada + plain + mixed.berry ))
head(yo)

ggplot(yo, aes(all.purchases)) +
  geom_histogram(binwidth = 1, fill = "blue")
```

***

### Prices over Time
Notes:

```{r Prices over Time}

ggplot(yo, aes(time, price)) +
  geom_jitter(alpha = 1/4, shape = 21, fill = I("#F79420"))

```

***

### Sampling Observations
Notes:
×ÓÑù±¾
***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(123)
sample.ids <- sample(levels(yo$id), 16)


ggplot(subset(yo, id %in% sample.ids), aes(time, price)) +
  facet_wrap(~id) +
  geom_line() +
  geom_point(aes(size = all.purchases), shape = 1)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:
```{r}
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
pf_subset <- pf[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

